\chapter{Various}

\section{Intervals}
	\kactlimport{IntervalContainer.h}
	\kactlimport{IntervalCover.h}
	\kactlimport{ConstantIntervals.h}

% \section{Misc. algorithms}
	% \kactlimport{TernarySearch.h}

\section{Debugging tricks}
\verb@-Wl,-stack_size -Wl,1000000@ local stack size.

\verb@signal(SIGSEGV, [](int) { _Exit(0); });@ converts segfaults into Wrong Answers.
			Similarly one can catch SIGABRT (assertion failures) and SIGFPE (zero divisions).

\verb@_GLIBCXX_DEBUG@ failures generate SIGABRT (or SIGSEGV on gcc 5.4.0 apparently).

\verb@feenableexcept(29);@ kills the program on NaNs (\texttt 1), 0-divs (\texttt 4), infinities (\texttt 8) and denormals (\texttt{16}).

\section{Optimization tricks}
	\verb@__builtin_ia32_ldmxcsr(40896);@ disables denormals (which make floats 20x slower near their minimum value).
	\subsection{Bit hacks}
		\verb@x & -x@ is the least bit in \texttt{x}.
		
		\verb@for (int x = m; x; ) { --x &= m; ... }@ loops over all subset masks of \texttt{m} (except \texttt{m} itself).
		
		\verb@c = x&-x, r = x+c; (((r^x) >> 2)/c) | r@ is the next number after \texttt{x} with the same number of bits set.
		
	\subsection{Pragmas}
		\verb@#pragma GCC optimize ("Ofast")@ will make GCC auto-vectorize loops and optimizes floating points better.
		
		\verb@#pragma GCC target ("avx2")@ can double performance of vectorized code, but causes crashes on old machines.
		
		\verb@#pragma GCC optimize ("trapv")@ kills the program on integer overflows (but is really slow).
	\kactlimport{FastMod.h}
	\kactlimport{FastInput.h}
	\kactlimport{BumpAllocator.h}
	\kactlimport{SmallPtr.h}
	\kactlimport{BumpAllocatorSTL.h}
	\kactlimport{pragma.h}
	\import{BitOps.tex}
	% \kactlimport{Unrolling.h}
	% \kactlimport{SIMD.h}
	\kactlimport[-l raw]{troubleshoot.txt}
	\kactlimport[-l raw]{practice.txt}
